Pillar 2 - Topic Modeling

### 2019-04-12 Pillar_2_-_Topic_Modeling.Rmd
changes to Topic Models

  nstart = 20,
  seed   = 1 : 20,
  best   = TRUE,

@@

```
###Training Models
We train the LDA for different numbers of topics (5 to 250 by 5), we save the resulting 50 models under `topic_model`, along with the DTM used to build the model, the corpus of origin (overview or manuals), the word and topic distributions results from that model, it's evaluation measures, and vectors of words and topics that allow us humans to get a feel of the model, along with some key words.
```{r LDA fit, cache = TRUE, eval = TRUE}
topic_numbers <- seq(from = 4, to = 150, by = 2)

@@

  ) %>%
  mutate(Origin     = rep(c("catalogues", "manuals"), 74),         # should be 50
         `Topic ID` = paste(Origin, n_topic, sep = "_"),

@@

# Clean workspace

@@

##Plots - Model Evaluation
To evaluate how many topics are optiomal, we graph the perplexity and log Likelihood of models against the number of topics.
```{r perplexity plots, eval = TRUE}
#Function
plot_evaluation <- function(origin){

>>>>

  nstart = 10,
  seed   = 1 : 10,
  best   = TRUE,

@@

```
###Training Models
We train the LDA for different numbers of topics (5 to 250 by 5), we save the resulting 50 models under `topic_model`, along with the DTM used to build the model, the corpus of origin (overview or manuals), the word and topic distributions results from that model, it's evaluation measures, and vectors of words and topics that allow us humans to get a feel of the model, along with some key words.
```{r LDA fit, cache = TRUE, eval = TRUE}
initial_time <- Sys.time()
topic_numbers <- seq(from = 4, to = 8, by = 2)

@@

  ) %>%
  mutate(Origin     = rep(c("catalogues", "manuals"), length(topic_numbers)),         # should be 50
         `Topic ID` = paste(Origin, n_topic, sep = "_"),

@@

final_time <- Sys.time()
took_how_long <- final_time - initial_time
# Clean workspace

@@

```{r print how long it takes}
(took_how_long)
```
##Plots - Model Evaluation
To evaluate how many topics are optiomal, we graph the perplexity and log Likelihood of models against the number of topics.
```{r perplexity plots, eval = TRUE}
#Function
plot_evaluation <- function(origin){
